Towards Verifying the Bitcoin-S Library

### 2019-06-25 paper/paper.tex
more intro
remove irrelevant stainless messages

@@

\todo{kai: do you need more explanation?}

@@

Stainless output:
\begin{lstlisting}[style=stainless]
[Warning ] currency/CurrencyUnits.scala:36:3: Could not extract tree in class: case private class SatoshisImpl extends Satoshis with Product with Serializable {
[Warning ]   <caseaccessor> <paramaccessor> private[this] val underlying: addition.modified.number.Int64 = _;
[Warning ]   <stable> <caseaccessor> <accessor> <paramaccessor> def underlying: addition.modified.number.Int64 = SatoshisImpl.this.underlying;
[Warning ]   def <init>(underlying: addition.modified.number.Int64): addition.modified.currency.Satoshis.SatoshisImpl = {
[Warning ]     SatoshisImpl.super.<init>();
[Warning ]     ()
[Warning ]   };
[Warning ]   <synthetic> def copy(underlying: addition.modified.number.Int64 = underlying): addition.modified.currency.Satoshis.SatoshisImpl = new SatoshisImpl(underlying);
[Warning ]   <synthetic> def copy$default$1: addition.modified.number.Int64 = SatoshisImpl.this.underlying;
[Warning ]   override <synthetic> def productPrefix: String = "SatoshisImpl";
[Warning ]   <synthetic> def productArity: Int = 1;
[Warning ]   <synthetic> def productElement(x$1: Int): Any = x$1 match {
[Warning ]     case 0 => SatoshisImpl.this.underlying
[Warning ]     case _ => throw new IndexOutOfBoundsException(x$1.toString())
[Warning ]   };
[Warning ]   override <synthetic> def productIterator: Iterator[Any] = runtime.this.ScalaRunTime.typedProductIterator[Any](SatoshisImpl.this);
[Warning ]   <synthetic> def canEqual(x$1: Any): Boolean = x$1.$isInstanceOf[addition.modified.currency.Satoshis.SatoshisImpl]();
[Warning ]   override <synthetic> def hashCode(): Int = ScalaRunTime.this._hashCode(SatoshisImpl.this);
[Warning ]   override <synthetic> def toString(): String = ScalaRunTime.this._toString(SatoshisImpl.this);
[Warning ]   override <synthetic> def equals(x$1: Any): Boolean = SatoshisImpl.this.eq(x$1.asInstanceOf[Object]).||(x$1 match {
[Warning ]   case (_: addition.modified.currency.Satoshis.SatoshisImpl) => true
[Warning ]   case _ => false
[Warning ] }.&&({
[Warning ]     <synthetic> val SatoshisImpl$1: addition.modified.currency.Satoshis.SatoshisImpl = x$1.asInstanceOf[addition.modified.currency.Satoshis.SatoshisImpl];
[Warning ]     SatoshisImpl.this.underlying.==(SatoshisImpl$1.underlying).&&(SatoshisImpl$1.canEqual(SatoshisImpl.this))
[Warning ]   }))
[Warning ] } (class scala.reflect.internal.Trees$ClassDef)
              private case class SatoshisImpl(underlying: Int64) extends Satoshis
              ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
\end{lstlisting}

And:
\begin{lstlisting}[style=stainless]
[Warning ] number/NumberType.scala:59:3: Could not extract tree in class: case private class Int64Impl extends Int64 with Product with Serializable {
[Warning ]   <caseaccessor> <paramaccessor> private[this] val underlying: BigInt = _;
[Warning ]   <stable> <caseaccessor> <accessor> <paramaccessor> def underlying: BigInt = Int64Impl.this.underlying;
[Warning ]   def <init>(underlying: BigInt): addition.modified.number.Int64.Int64Impl = {
[Warning ]     Int64Impl.super.<init>();
[Warning ]     ()
[Warning ]   };
[Warning ]   scala.this.Predef.require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(-9223372036854775808L)), "Number was too small for a int64, got: ".+(Int64Impl.this.underlying));
[Warning ]   scala.this.Predef.require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(9223372036854775807L)), "Number was too big for a int64, got: ".+(Int64Impl.this.underlying));
[Warning ]   <synthetic> def copy(underlying: BigInt = underlying): addition.modified.number.Int64.Int64Impl = new Int64Impl(underlying);
[Warning ]   <synthetic> def copy$default$1: BigInt = Int64Impl.this.underlying;
[Warning ]   override <synthetic> def productPrefix: String = "Int64Impl";
[Warning ]   <synthetic> def productArity: Int = 1;
[Warning ]   <synthetic> def productElement(x$1: Int): Any = x$1 match {
[Warning ]     case 0 => Int64Impl.this.underlying
[Warning ]     case _ => throw new IndexOutOfBoundsException(x$1.toString())
[Warning ]   };
[Warning ]   override <synthetic> def productIterator: Iterator[Any] = runtime.this.ScalaRunTime.typedProductIterator[Any](Int64Impl.this);
[Warning ]   <synthetic> def canEqual(x$1: Any): Boolean = x$1.$isInstanceOf[addition.modified.number.Int64.Int64Impl]();
[Warning ]   override <synthetic> def hashCode(): Int = ScalaRunTime.this._hashCode(Int64Impl.this);
[Warning ]   override <synthetic> def toString(): String = ScalaRunTime.this._toString(Int64Impl.this);
[Warning ]   override <synthetic> def equals(x$1: Any): Boolean = Int64Impl.this.eq(x$1.asInstanceOf[Object]).||(x$1 match {
[Warning ]   case (_: addition.modified.number.Int64.Int64Impl) => true
[Warning ]   case _ => false
[Warning ] }.&&({
[Warning ]     <synthetic> val Int64Impl$1: addition.modified.number.Int64.Int64Impl = x$1.asInstanceOf[addition.modified.number.Int64.Int64Impl];
[Warning ]     Int64Impl.this.underlying.==(Int64Impl$1.underlying).&&(Int64Impl$1.canEqual(Int64Impl.this))
[Warning ]   }))
[Warning ] } (class scala.reflect.internal.Trees$ClassDef)
              private case class Int64Impl(underlying: BigInt) extends Int64 {
              ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
\end{lstlisting}

@@

\todo{kai special chars from stainless output what now?}
% \begin{lstlisting}[style=stainless][Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @33:39...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
% [  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
% [  Info  ] Cache hit: 'adt invariant' VC for apply @33:39...
% [  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
% [  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
% [Warning ]  => INVALID
% [Warning ] Found counter-example:
% [Warning ]   bigInt: BigInt -> -9223372036854775809
% [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
% [Warning ]  => INVALID
% [Warning ] Found counter-example:
% [Warning ]   num: Number   -> Int64Impl(9223372036854775807)
% [Warning ]   thiss: Number -> Int64Impl(1)
% [  Info  ]   ┌───────────────────┐
% [  Info  ] ╔═╡ stainless summary ╞══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
% [  Info  ] ║ └───────────────────┘                                                                                                                      ║
% [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid           U:smt-z3  number/NumberType.scala:17:36       0.110 ║
% [  Info  ] ║ apply  adt invariant                                                 valid from cache            currency/CurrencyUnits.scala:33:39  1.136 ║
% [  Info  ] ║ apply  adt invariant                                                 invalid           U:smt-z3  number/NumberType.scala:62:38       0.394 ║
% [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
% [  Info  ] ║ total: 3    valid: 1    (1 from cache) invalid: 2    unknown: 0    time:   1.640                                                           ║
% [  Info  ] ╚════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
% [  Info  ] Shutting down executor service.  
% \end{lstlisting}

@@

Stainless output now: \todo{kai special chars again}
% \begin{lstlisting}[style=stainless]
% [Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
% [  Info  ]  - Checking cache: 'postcondition' VC for + @12:3...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @34:39...
% [  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
% [  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
% [  Info  ] Cache hit: 'adt invariant' VC for apply @34:39...
% [  Info  ] Cache hit: 'postcondition' VC for + @12:3...
% [  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
% [  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
% [Warning ]  => INVALID
% [Warning ] Found counter-example:
% [Warning ]   bigInt: BigInt -> -9223372036854775809
% [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
% [  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
% [Warning ]  => INVALID
% [Warning ] Found counter-example:
% [Warning ]   num: Number   -> Int64Impl(9223372036854775807)
% [Warning ]   thiss: Number -> Int64Impl(1)
% [  Info  ]   ┌───────────────────┐
% [  Info  ] ╔═╡ stainless summary ╞══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
% [  Info  ] ║ └───────────────────┘                                                                                                                      ║
% [  Info  ] ║ +      postcondition                                                 valid from cache            currency/CurrencyUnits.scala:12:3   1.266 ║
% [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid           U:smt-z3  number/NumberType.scala:17:36       0.089 ║
% [  Info  ] ║ apply  adt invariant                                                 valid from cache            currency/CurrencyUnits.scala:34:39  0.194 ║
% [  Info  ] ║ apply  adt invariant                                                 invalid           U:smt-z3  number/NumberType.scala:62:38       0.348 ║
% [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
% [  Info  ] ║ total: 4    valid: 2    (2 from cache) invalid: 2    unknown: 0    time:   1.897                                                           ║
% [  Info  ] ╚════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
% [  Info  ] Shutting down executor service.
% \end{lstlisting}

@@

% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}

% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%

>>>>

\todo{anna: stainless unterstützt anscheinend type bounds prinzipiell
  (nur nicht selbstreferenzierende)? siehe B.4, stainless issue 519}

@@

@@

Stainless output:
\begin{lstlisting}[style=stainless]
[Warning ] currency/CurrencyUnits.scala:36:3: Could not extract tree in class: case private class SatoshisImpl extends Satoshis with Product with Serializable {
...
[Warning ] } (class scala.reflect.internal.Trees$ClassDef)
              private case class SatoshisImpl(underlying: Int64) extends Satoshis
              ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
\end{lstlisting}

And:
\begin{lstlisting}[style=stainless]
[Warning ] number/NumberType.scala:59:3: Could not extract tree in class: case private class Int64Impl extends Int64 with Product with Serializable {
...
[Warning ] } (class scala.reflect.internal.Trees$ClassDef)
              private case class Int64Impl(underlying: BigInt) extends Int64 {
              ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
\end{lstlisting}

@@

\begin{lstlisting}[style=stainless]
[  Info  ]  - Checking cache: 'adt invariant' VC for apply @33:39...
[  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
[  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
[  Info  ] Cache hit: 'adt invariant' VC for apply @33:39...
[  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
[  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   bigInt: BigInt -> -9223372036854775809
[  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
[  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
[  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
[  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   num: Number   -> Int64Impl(9223372036854775807)
[Warning ]   thiss: Number -> Int64Impl(1)
\end{lstlisting}

@@

Stainless output now:
\begin{lstlisting}[style=stainless]
[  Info  ]  - Checking cache: 'postcondition' VC for + @12:3...
[  Info  ]  - Checking cache: 'adt invariant' VC for apply @34:39...
[  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
[  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
[  Info  ] Cache hit: 'adt invariant' VC for apply @34:39...
[  Info  ] Cache hit: 'postcondition' VC for + @12:3...
[  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
[  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   bigInt: BigInt -> -9223372036854775809
[  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
[  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
[  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
[  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   num: Number   -> Int64Impl(9223372036854775807)
[Warning ]   thiss: Number -> Int64Impl(1)
\end{lstlisting}

@@
